### 2021-06-27 docs/submission/srep/coverletter/letter-tex/covlet.tex
updates cover letter matching title

%* The affiliation and contact information of your corresponding author
I have the pleasure of sending you the manuscript entitled "Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities" authored by Miguel Xochicale and Chris Baber from the University of Birmingham to be considered for publication as a research article in your prestigious journal.

>>>>

%* The affiliation and contact information of your corresponding author
I have the pleasure of sending you the manuscript entitled 
"Recurrence Quantification Analysis to quantify Movement Variability in Human-Humanoid Interaction Activities"
authored by Miguel Xochicale and Chris Baber from the University of Birmingham to be considered for publication as a research article in your prestigious journal.
